Gelation as a condensation frustrated by hydrodynamics and mechanical tension

### 2015-07-24 gel_cond/trunk/paper.tex
insert fig:hydro

>>>>

\subsection*{Role of hydrodynamics}

\begin{figure}
	\includegraphics{figs/hydro.pdf}
	\caption{\textbf{Hydrodynamics} \textbf{a} Evolution of triplet radii of gyration in a non percolating sample ($\phi=4~\%$, $c_p=\SI{1}{\gram\per\litre}$). The characteristic time to reach the stable compact cluster is much longer than the Brownian time. \textbf{b} Evolution of the aspect ratios of clusters of 4 particles and more in the same sample (dashed lines) and in a percolating sample ($\phi=8~\%$, $c_p=\SI{1.5}{\gram\per\litre}$, continuous lines) \textbf{c} Bond angle distribution relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue) obtained in the percolating sample. Future bonds are shifted to smaller angles, whereas gas adsorption takes place from larger angles. Insets sketch both cases, with present bonds drawn thick and future bonds drawn dotted.}
	\label{fig:hydro}
\end{figure}

In Figure~\ref{fig:hydro}a, we follow the compaction of clusters made of only three particles in a non percolating sample.
